Methods for Large Scale Learning to Rank

### 2014-09-23 report/Chapters/Implementation.tex
naar refactoring werk

\subsection{Training}
The Pig jobs that form the ListNet training phase form an implementation of the theoretical description of ListNet as described in section \ref{sec:ltrmethods_listnet}. The training stage, like the preprocessing stage, consists of two separate Pig jobs. The first Pig job calculates the Cross Entropy loss on training data of the current model and calculates the gradients for the next model update. The second Pig job is an internal validation step that validates the model on the validation set by calculating \ac{nDCG}@k.\\

@@

\begin{table}
\centering
\begin{tabular}{p{6cm}p{7cm}}\toprule
UDF & Description \\
\midrule
udf.util.Ndcg() & Calculates \ac{nDCG}@k for a query.\\
\bottomrule
\end{tabular}
\caption{Description of training phase User Defined Functions (Pig job 2)}
\label{tbl:training_udfs_2}
\end{table}

\subsection{Testing}
The testing stage tests the best model found in the training iterations, selected on validation set \ac{nDCG}@k (as calculated in the second Pig job of the training stage), by calculating the \ac{nDCG}@k of this model on the test set.\\

>>>>

\subsection{Training}
The Pig jobs that form the ListNet training phase form an implementation of the theoretical description of ListNet as described in section \ref{sec:ltrmethods_listnet}. The training stage, like the preprocessing stage, consists of two separate Pig jobs. The first Pig job calculates the Cross Entropy loss on training data of the current model and calculates the gradients for the next model update. The second Pig job is an internal validation step that validates the model on the validation set by calculating \ac{NDCG}@k.\\

@@

\begin{table}
\centering
\begin{tabular}{p{6cm}p{7cm}}\toprule
UDF & Description \\
\midrule
udf.util.Ndcg() & Calculates \ac{NDCG}@k for a query.\\
\bottomrule
\end{tabular}
\caption{Description of training phase User Defined Functions (Pig job 2)}
\label{tbl:training_udfs_2}
\end{table}

\subsection{Testing}
The testing stage tests the best model found in the training iterations, selected on validation set \ac{NDCG}@k (as calculated in the second Pig job of the training stage), by calculating the \ac{NDCG}@k of this model on the test set.\\

### 2014-09-23 report/Chapters/Introduction.tex
naar refactoring werk

Research in the field of ranking models has for a long time been based on manually designed ranking functions, such as the well-known BM25 model \cite{Robertson1994}. Luhn \cite{Luhn1957} was the first to propose a model that assigned relevance scores to documents given a query back in 1957. The increasing amounts of potential training data have recently made it possible to leverage machine learning methods to obtain more effective models. Learning-to-Rank is the relatively new research area that covers the use of machine learning models for the ranking task.\\

In recent years several Learning-to-Rank benchmark datasets have been proposed that enable comparison of the performance of different Learning-to-Rank methods. Well-known benchmark datasets include the \emph{Yahoo! Learning to Rank Challenge} dataset \cite{Chapelle2011a}, the Yandex Internet Mathematics competition\footnote{http://imat-relpred.yandex.ru/en/}, and the LETOR dataset \cite{Qin2010} that was published by Microsoft Research. One of the concluding observations of the \emph{Yahoo! Learning to Rank Challenge} was that almost all work in the Learning-to-Rank field focuses on ranking accuracy, while efficiency and scalability of Learning-to-Rank algorithms is still an underexposed research area that is likely to become more important in the near future as training sets are becoming larger and larger \cite{Chapelle2011b}. Liu \cite{Liu2007} confirms the observation that efficiency and scalability of Learning-to-Rank methods has so far been an overlooked research area in his influential book on Learning-to-Rank.\\

Some research has been done in the area of parallel or distributed machine learning \cite{Chu2007,Chang2007}. However, almost none of these studies include the Learning-to-Rank sub-field of machine learning. The field of efficient Learning-to-Rank has been getting some attention lately \cite{Asadi2013a,Asadi2013b,Busa-Fekete2012,Sousa2012,Shukla2012}, since Liu \cite{Liu2007} first stated its growing importance back in 2007. Only several of these studies \cite{Sousa2012,Shukla2012} have explored the possibilities of efficient Learning-to-Rank through the use of parallel programming paradigms.\\

MapReduce \cite{Dean2004} is a parallel programming framework that is inspired by the \emph{Map} and \emph{Reduce} functions commonly used in functional programming. Since Google developed the MapReduce parallel programming framework back in 2004 it has grown to be the industry standard model for parallel programming. Lin \cite{Lin2013} observed that algorithms that are of iterative nature, which most Learning-to-Rank algorithms are, are not amenable to the MapReduce framework. Lin argued that as a solution to the non-amenability of iterative algorithms to the MapReduce framework, iterative algorithms can often be replaced with non-iterative alternatives or can still be optimized in such a way that its performance in a MapReduce setting is good enough. Alternative programming models are argued against by Lin, as they lack the critical mass as the data processing framework of choice.\\

The appearance of benchmark datasets gave insight in the performance of different Learning-to-Rank approaches, which resulted in increasing popularity of those methods that showed to perform well on one or more benchmark datasets. Up to now it remains unknown whether popular existing Learning-to-Rank methods scale well when they are used in a parallel manner using the MapReduce framework. This thesis aims to be an exploratory start in this little researched area of parallel Learning-to-Rank. A more extensive overview of my research goals and questions are described in section \ref{sec:goals}.\\

\section{Research Goals}
\label{sec:goals}
The objective of this thesis is to explore the speed-up in execution time of Learning-to-Rank algorithms through parallelisation using the MapReduce framework.
This work focuses on those Learning-to-Rank algorithms that have shown leading performance on relevant benchmark datasets.
This thesis addresses the following research questions:
\begin{description}
\item[RQ1] What are the best performing Learning-to-Rank algorithms in terms of accuracy on relevant benchmark datasets?\\

\item[RQ2] What is the speed-up of those Learning-to-Rank algorithms when executed using the MapReduce framework?\\
Where the definition of \emph{relative speed-up} is used for speed-up \cite{Sun1991}:\\

@@

\section{Approach}
\subsection{Methodology for Research Question I}
A literature study will be performed to get insight in relevant existing techniques for large scale Learning-to-Rank. The literature study will be performed by using the following query:\\

@@

The query incorporates different ways of writing of Learning-to-Rank, with and without hyphens, and the synonymous term \emph{machine learned ranking} to increase search recall, i.e. to make sure that no relevant studies are missed. For the same reason the terms \emph{parallel} and \emph{distributed} are included in the search query. Even though \emph{parallel} and \emph{distributed} are not always synonymous is all definitions, we are interested in both approaches in non-sequential data processing.\\

@@

\subsection{Methodology for Research Question II}
\label{ssec:rq2_methodology}
To find an answer to the second research question, the Learning-to-Rank methods determined in the first research question will be implemented in the MapReduce framework and training time will be measured as a factor of the number of cluster nodes used to perform the computation. The HDInsight cloud-based MapReduce platform from Microsoft will be used to run the Learning-to-Rank algorithms on. HDInsight is based on the popular open source MapReduce implementation Hadoop\footnote{http://hadoop.apache.org/}.\\

@@

\begin{description}
\item[Chapter II: Background]{introduces the reader to the basic principles and recent work in the fields of Learning-to-Rank.}
\item[Chapter III: Related Work]{concisely describes existing work in the field of parallel Learning-to-Rank.}
\item[Chapter IV: Benchmark Results]{sketches the accuracy of existing Learning-to-Rank methods on several benchmark datasets and describes the selection of Learning-to-Rank methods for the parallelisation experiments.}
\item[Chapter V: Selected Learning-to-Rank Methods]{describes the algorithms and details of the Learning-to-Rank methods selected in Chapter IV.}
\item[Chapter VI: Implementation]{describes implementation details of the Learning-to-Rank algorithms in the Hadoop framework.}
\item[Chapter VII: Results \& Discussion]{presents and discusses speed-up results for the implemented Learning-to-Rank methods.}
\item[Chapter VIII: Conclusion]{summarizes the results and answers our research questions based on the results. The limitations of our research as well as future research directions in the field are mentioned here.}
\end{description}

>>>>

Research in the field of ranking models has for a long time been based on manually designed ranking functions, such as the well-known BM25 model \cite{Robertson1994}. Luhn \cite{Luhn1957} was the first to propose a model that assigned relevance scores to documents given a query back in 1957. The increasing amounts of potential training data have recently made it possible to leverage machine learning methods to obtain more effective models. Learning to Rank is the relatively new research area that covers the use of machine learning models for the ranking task.\\

In recent years several Learning to Rank benchmark datasets have been proposed that enable comparison of the performance of different Learning to Rank methods. Well-known benchmark datasets include the \emph{Yahoo! Learning to Rank Challenge} dataset \cite{Chapelle2011a}, the Yandex Internet Mathematics competition\footnote{http://imat-relpred.yandex.ru/en/}, and the LETOR dataset \cite{Qin2010} that was published by Microsoft Research. One of the concluding observations of the \emph{Yahoo! Learning to Rank Challenge} was that almost all work in the Learning to Rank field focuses on ranking accuracy, while efficiency and scalability of Learning to Rank algorithms is still an underexposed research area that is likely to become more important in the near future as training sets are becoming larger and larger \cite{Chapelle2011b}. Liu \cite{Liu2007} confirms the observation that efficiency and scalability of Learning to Rank methods has so far been an overlooked research area in his influential book on Learning to Rank.\\

Some research has been done in the area of parallel or distributed machine learning \cite{Chu2007,Chang2007}. However, almost none of these studies include the Learning to Rank sub-field of machine learning. The field of efficient Learning to Rank has been getting some attention lately \cite{Asadi2013a,Asadi2013b,Busa-Fekete2012,Sousa2012,Shukla2012}, since Liu \cite{Liu2007} first stated its growing importance back in 2007. Only several of these studies \cite{Sousa2012,Shukla2012} have explored the possibilities of efficient Learning to Rank through the use of parallel programming paradigms.\\

MapReduce \cite{Dean2004} is a parallel programming framework that is inspired by the \emph{Map} and \emph{Reduce} functions commonly used in functional programming. Since Google developed the MapReduce parallel programming framework back in 2004 it has grown to be the industry standard model for parallel programming. Lin \cite{Lin2013} observed that algorithms that are of iterative nature, which most Learning to Rank algorithms are, are not amenable to the MapReduce framework. Lin argued that as a solution to the non-amenability of iterative algorithms to the MapReduce framework, iterative algorithms can often be replaced with non-iterative alternatives or can still be optimized in such a way that its performance in a MapReduce setting is good enough. Alternative programming models are argued against by Lin, as they lack the critical mass as the data processing framework of choice.\\

The appearance of benchmark datasets gave insight in the performance of different Learning to Rank approaches, which resulted in increasing popularity of those methods that showed to perform well on one or more benchmark datasets. Up to now it remains unknown whether popular existing Learning to Rank methods scale well when they are used in a parallel manner using the MapReduce framework. This thesis aims to be an exploratory start in this little researched area of parallel Learning to Rank. A more extensive overview of my research goals and questions are described in section \ref{sec:goals}.\\

\section{Research Goals}
\label{sec:goals}
The objective of this thesis is to explore the speed-up in execution time of Learning to Rank algorithms through parallelisation using the MapReduce framework.
This work focuses on those Learning to Rank algorithms that have shown leading performance on relevant benchmark datasets.
This thesis addresses the following research questions:
\begin{description}
\item[RQ1] What are the best performing Learning to Rank algorithms in terms of accuracy on relevant benchmark datasets?\\

\item[RQ2] What is the speed-up of those Learning to Rank algorithms when executed using the MapReduce framework?\\
Where the definition of \emph{relative speed-up} is used for speed-up \cite{Sun1991}:\\

@@

\section{Approach}
\subsection{Methodology for Research Question I}
A literature study will be performed to get insight in relevant existing techniques for large scale Learning to Rank. The literature study will be performed by using the following query:\\

@@

The query incorporates different ways of writing of Learning to Rank, with and without hyphens, and the synonymous term \emph{machine learned ranking} to increase search recall, i.e. to make sure that no relevant studies are missed. For the same reason the terms \emph{parallel} and \emph{distributed} are included in the search query. Even though \emph{parallel} and \emph{distributed} are not always synonymous is all definitions, we are interested in both approaches in non-sequential data processing.\\

@@

\subsection{Methodology for Research Question II}
\label{ssec:rq2_methodology}
To find an answer to the second research question, the Learning to Rank methods determined in the first research question will be implemented in the MapReduce framework and training time will be measured as a factor of the number of cluster nodes used to perform the computation. The HDInsight cloud-based MapReduce platform from Microsoft will be used to run the Learning to Rank algorithms on. HDInsight is based on the popular open source MapReduce implementation Hadoop\footnote{http://hadoop.apache.org/}.\\

@@

\begin{description}
\item[Chapter II: Background]{introduces the reader to the basic principles and recent work in the fields of Learning to Rank.}
\item[Chapter III: Related Work]{concisely describes existing work in the field of parallel Learning to Rank.}
\item[Chapter IV: Benchmark Results]{sketches the accuracy of existing Learning to Rank methods on several benchmark datasets and describes the selection of Learning to Rank methods for the parallelisation experiments.}
\item[Chapter V: Selected Learning to Rank Methods]{describes the algorithms and details of the Learning to Rank methods selected in Chapter IV.}
\item[Chapter VI: Implementation]{describes implementation details of the Learning to Rank algorithms in the Hadoop framework.}
\item[Chapter VII: Results \& Discussion]{presents and discusses speed-up results for the implemented Learning to Rank methods.}
\item[Chapter VIII: Conclusion]{summarizes the results and answers our research questions based on the results. The limitations of our research as well as future research directions in the field are mentioned here.}
\end{description}

### 2014-09-23 report/Chapters/LTRMethods.tex
naar refactoring werk

\label{chap:ltr_methods}
The learning algorithms of the well-performing Learning-to-Rank methods selected in Chapter \ref{chap:cross_comparison} are presented and explained in this Chapter. The Learning-to-Rank methods will be discussed in order of an increasing degree of certainty and decreasing ranking accuracy, as concluded in Chapter \ref{chap:cross_comparison}.

@@

\section{SmoothRank}
SmoothRank \cite{Chapelle2010} is a listwise ranking method that, in contrast to ListNet, directly optimises an information retrieval evaluation measure. SmoothRank enables direct optimisation of the non-convex and discontinuous evaluation measure by smoothing, that is, approximating the rank position. In this section, I apply the SmoothRank approximation method to the \ac{nDCG} evaluation measure for illustration, but the same procedure can be applied to \ac{MAP} or any other information retrieval measure. The smoothing function used in SmoothRank is based on the softmax activation function \cite{Bridle1990}, which is often used in neural networks. The softmax function is formally defined as shown in Equation \ref{eq:softmax_algorithm}.
\begin{equation}
p_i = \frac{e^{f_i/\sigma}}{\sum\nolimits_{j=1}^{m}e^{f_j/\sigma}}
\label{eq:softmax_algorithm}
\end{equation}

where $\sigma$ is the smoothing parameter. Chapelle et al. \cite{Chapelle2010} apply this softmax function to the \ac{nDCG} formula and hereby introduce a soft version of indicator variable $h_{i,j}$ through the computation shown in Equation \ref{eq:soft_ndcg}.

\begin{equation}
h_{i,j} = e^{-\frac{(f(x_i))-(f(x_{d(j)}))^2}{\sigma}}\Big/\sum\nolimits_{k=1}^{m}e^{-\frac{(f(x_k))-f(x_{d(j)})^2}{\sigma}}
\label{eq:soft_ndcg}
\end{equation}

It can be shown that the derivative of the smoothed \ac{nDCG} version shown in Equation \ref{eq:soft_ndcg} and the smoothed versions of other \ac{IR} metrics can be calculated in $\mathcal{O}(m^2)$, which enable fast gradient descent optimisation. The optimisation step in SmoothRank uses the nonlinear conjugate gradient method  with Polak-Ribiere update \cite{Shewchuk1994}, which is a type of gradient descent method. This optimisation method is prone to local optima, which is alleviated by adding a pre-calculated, better than naive, starting point and by adding a regularisation term.\\

@@

The choice of the smoothing parameter $\sigma$ in Equation \ref{eq:soft_ndcg} is important, because a too small value makes the function more non-smooth and therefore harder to optimise, while a too large value results in a optimisation function with optima that substantially differ from the true optimal rankings. To deal with the problem of choosing the smoothing parameter, SmoothRank uses an annealing method where the optimisation procedure starts with a large $\sigma$ and iteratively reduces it by dividing it by two at each iteration. Algorithm \ref{alg:smoothrank} shows the algorithm that summarises all steps of the SmoothRank method.\\
\LinesNumbered
\begin{algorithm}[H]
 Find an initial solution $w_0$ (by regression or Rank\acs{SVM}).\\
 Set $w = w_0$ and $\sigma$ to a large value.\\
 \While{Stopping condition not satisfied}{
 	 Starting from $w$, minimize by non-linear conjugate gradient descent:
 	 $\lambda||w-w_0||_2 - \sum\nolimits_{q}A_q(w,\sigma)$\\
 	 $\sigma = \sigma/2$
 }
 \caption{Learning algorithm of SmoothRank, obtained from \cite{Chapelle2010}}
 \label{alg:smoothrank}
\end{algorithm}

\section{FenchelRank}
FenchelRank \cite{Lai2013} is a ranking method that addresses the sparse Learning-to-Rank problem, which is the problem of learning a ranking function with only a few non-zero coefficients with respect to the input features. FenchelRank is based on the theory of Fenchel Duality \cite{Rifkin2007} and uses a generic algorithm framework proposed by Shalev-Shwartz and Singer \cite{Shalev-Shwartz2010}. FenchelRank optimises the objective function shown in Equation \ref{eq:pairwise_l1_loss} which is equivalent to the standard pairwise loss function with $\ell_1$-norm regularisation. The $\ell_1$-norm regularisation function in this equation is represented by $||x||_1$ and is defined as $||x||_1=\sum\nolimits_i|x_i|$.
\begin{equation}
\min_w G(w) = \min_w I_{||w||_{1} \le 1}(w) + \frac{r^2}{p} \sum\limits_{i=1}^{p}\max(0,\frac{1}{r}-(Kw)_i)^2
\label{eq:pairwise_l1_loss}
\end{equation}

@@

\section{FSMRank}
Lai et al. \cite{Lai2013c} observed that existing feature selection methods in Learning-to-Rank all follow a two-stage paradigm consisting of a first stage of selecting a subset of features from the original features, followed by a second stage where a ranking model learnt based on the selected features. Lai et al. \cite{Lai2013c} state it as a limitation of this paradigm that the selected features in the first step are not necessarily the optimal features for the second stage where the ranking model is build. FSMRank \cite{Lai2013c} addresses this limitation by formulating a joint convex optimisation function that minimises ranking errors while simultaneously selecting a subset of features.\\

@@

\section{LRUF}
LRUF \cite{Torkestani2012b} is Learning-to-Rank method based on the theory of learning automata. Learning automata are adaptive decision-making units that learn the optimal set of actions through repeated interactions with its environment. Variable structure learning automata can be defined as a triple $<\beta,\alpha,L>$, with $\beta$ being the set of inputs, $\alpha$ the set of actions. $L$, the learning algorithm ,is a recurrence relation that modifies the action probability vector of the actions in $\alpha$.\\

>>>>

\label{chap:ltr_methods}
The learning algorithms of the well-performing Learning to Rank methods selected in Chapter \ref{chap:cross_comparison} are presented and explained in this Chapter. The Learning to Rank methods will be discussed in order of an increasing degree of certainty and decreasing ranking accuracy, as concluded in Chapter \ref{chap:cross_comparison}.

@@

\section{SmoothRank}
SmoothRank \cite{Chapelle2010} is a listwise ranking method that, in contrast to ListNet, directly optimises an information retrieval evaluation measure. SmoothRank enables direct optimisation of the non-convex and discontinuous evaluation measure by smoothing, that is, approximating the rank position. In this section, I apply the SmoothRank approximation method to the \ac{NDCG} evaluation measure for illustration, but the same procedure can be applied to \ac{MAP} or any other information retrieval measure. The smoothing function used in SmoothRank is based on the softmax activation function \cite{Bridle1990}, which is often used in neural networks. The softmax function is formally defined as shown in Equation \ref{eq:softmax_algorithm}.
\begin{equation}
p_i = \frac{e^{f_i/\sigma}}{\sum\nolimits_{j=1}^{m}e^{f_j/\sigma}}
\label{eq:softmax_algorithm}
\end{equation}

where $\sigma$ is the smoothing parameter. Chapelle et al. \cite{Chapelle2010} apply this softmax function to the \ac{NDCG} formula and hereby introduce a soft version of indicator variable $h_{i,j}$ through the computation shown in Equation \ref{eq:soft_NDCG}.

\begin{equation}
h_{i,j} = e^{-\frac{(f(x_i))-(f(x_{d(j)}))^2}{\sigma}}\Big/\sum\nolimits_{k=1}^{m}e^{-\frac{(f(x_k))-f(x_{d(j)})^2}{\sigma}}
\label{eq:soft_NDCG}
\end{equation}

It can be shown that the derivative of the smoothed \ac{NDCG} version shown in Equation \ref{eq:soft_NDCG} and the smoothed versions of other \ac{IR} metrics can be calculated in $\mathcal{O}(m^2)$, which enable fast gradient descent optimisation. The optimisation step in SmoothRank uses the nonlinear conjugate gradient method  with Polak-Ribiere update \cite{Shewchuk1994}, which is a type of gradient descent method. This optimisation method is prone to local optima, which is alleviated by adding a pre-calculated, better than naive, starting point and by adding a regularisation term.\\

@@

The choice of the smoothing parameter $\sigma$ in Equation \ref{eq:soft_NDCG} is important, because a too small value makes the function more non-smooth and therefore harder to optimise, while a too large value results in a optimisation function with optima that substantially differ from the true optimal rankings. To deal with the problem of choosing the smoothing parameter, SmoothRank uses an annealing method where the optimisation procedure starts with a large $\sigma$ and iteratively reduces it by dividing it by two at each iteration. Algorithm \ref{alg:smoothrank} shows the algorithm that summarises all steps of the SmoothRank method.\\
\LinesNumbered
\begin{algorithm}[H]
 Find an initial solution $w_0$ (by regression or Rank\acs{SVM}).\\
 Set $w = w_0$ and $\sigma$ to a large value.\\
 \While{Stopping condition not satisfied}{
 	 Starting from $w$, minimize by non-linear conjugate gradient descent:
 	 $\lambda||w-w_0||_2 - \sum\nolimits_{q}A_q(w,\sigma)$\\
 	 $\sigma = \sigma/2$
 }
 \caption{Learning algorithm of SmoothRank, obtained from \cite{Chapelle2010}}
 \label{alg:smoothrank}
\end{algorithm}

\section{FenchelRank}
FenchelRank \cite{Lai2013} is a ranking method that addresses the sparse Learning to Rank problem, which is the problem of learning a ranking function with only a few non-zero coefficients with respect to the input features. FenchelRank is based on the theory of Fenchel Duality \cite{Rifkin2007} and uses a generic algorithm framework proposed by Shalev-Shwartz and Singer \cite{Shalev-Shwartz2010}. FenchelRank optimises the objective function shown in Equation \ref{eq:pairwise_l1_loss} which is equivalent to the standard pairwise loss function with $\ell_1$-norm regularisation. The $\ell_1$-norm regularisation function in this equation is represented by $||x||_1$ and is defined as $||x||_1=\sum\nolimits_i|x_i|$.
\begin{equation}
\min_w G(w) = \min_w I_{||w||_{1} \le 1}(w) + \frac{r^2}{p} \sum\limits_{i=1}^{p}\max(0,\frac{1}{r}-(Kw)_i)^2
\label{eq:pairwise_l1_loss}
\end{equation}

@@

\section{FSMRank}
Lai et al. \cite{Lai2013c} observed that existing feature selection methods in Learning to Rank all follow a two-stage paradigm consisting of a first stage of selecting a subset of features from the original features, followed by a second stage where a ranking model learnt based on the selected features. Lai et al. \cite{Lai2013c} state it as a limitation of this paradigm that the selected features in the first step are not necessarily the optimal features for the second stage where the ranking model is build. FSMRank \cite{Lai2013c} addresses this limitation by formulating a joint convex optimisation function that minimises ranking errors while simultaneously selecting a subset of features.\\

@@

\section{LRUF}
LRUF \cite{Torkestani2012b} is Learning to Rank method based on the theory of learning automata. Learning automata are adaptive decision-making units that learn the optimal set of actions through repeated interactions with its environment. Variable structure learning automata can be defined as a triple $<\beta,\alpha,L>$, with $\beta$ being the set of inputs, $\alpha$ the set of actions. $L$, the learning algorithm ,is a recurrence relation that modifies the action probability vector of the actions in $\alpha$.\\
